Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2017-08-15 appendix.tex
add a reference and correct wording

where $y_i$ ($f_i$) is a measurement (model) in a centrality bin, and the systematic and statistical errors  are combined in quadrature $\sigma_i = \sqrt{\sigma_{i, stat}^2 + \sigma_{i, syst}^2}$.
The centrality range is restricted in 10--50\% bins, corresponding the total number of data sets in each observable (N) is 4.
The resulting ${\chi}^2$ for few selected calculations from three theoretical models which describe the SC observables best is shown in Fig.~\ref{fig:Figure_A5}.
\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.8\textwidth}{!}{\includegraphics{figs/chisq_bestfits.eps}}
        \caption{The ${\chi}^2$ values from the comparison of few selected calculations from three theoretical models are shown for all SC observables. Closed (open) markers are for SC($m$,$n$) (NSC($m$,$n$)).}
        \label{fig:Figure_A5}
              \end{center}
\end{figure*}

We found that in case of VISH2+1 calculations, the ${\chi}^2$ values of SC($m$,$n$) is larger than those of NSC($m$,$n$). This can be explained by the fact that the individual flow harmonics $v_n$ is not well described as shown in Fig.~\ref{fig:Figure_A4} compared to other models.
Even though the calculations from event-by-event EKRT+viscous hydrodynamics give best ${\chi}^2$ values both for SC($m$,$n$) and NSC($m$,$n$), the ${\chi}^2$
values are bit large especially for the observables related with $v_3$. 
Even with the best model calculations from three theoretical models, the ${\chi}^2$ value varies a lot depending both on the model parameters and/or different order SC observables, which implies that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties.

>>>>

where $y_i$ ($f_i$) is a measurement (model) in a centrality bin, and the systematic and statistical errors  are combined in quadrature $\sigma_i = \sqrt{\sigma_{i, stat}^2 + \sigma_{i, syst}^2}$.
The centrality range is restricted in 10--50\% bins, corresponding the total number of data sets in each observable (N) is 4.
The resulting ${\chi}^2$ for few selected calculations from three theoretical models which describe the SC observables best is shown in Fig.~\ref{fig:Figure_A5}.
\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.8\textwidth}{!}{\includegraphics{figs/chisq_bestfits.eps}}
        \caption{The ${\chi}^2$ values from the comparison of few selected calculations from three theoretical models are shown for all SC observables. The ${\chi}^2$ results for SC($m$,$n$) (NSC($m$,$n$)) are shown as closed (open) markers.}
        \label{fig:Figure_A5}
              \end{center}
\end{figure*}

We found that in case of the calculations from VISH2+1 and default AMPT models, the ${\chi}^2$ values for SC($m$,$n$) is larger than those for NSC($m$,$n$). This can be explained by the fact that the individual flow harmonics $v_n$ is not well described by those models compared to event-by-event EKRT+viscous hydrodynamics as shown in Fig.~\ref{fig:Figure_A4}.
Even though the calculations from event-by-event EKRT+viscous hydrodynamics give best ${\chi}^2$ values both for SC($m$,$n$) and NSC($m$,$n$), the ${\chi}^2$
values are large especially for the observables related with $v_3$. 
Even with the best model calculations from three theoretical models, the ${\chi}^2$ value varies a lot depending both on the model parameters and/or different order SC observables, which implies that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties used in the model calculations.

### 2017-08-15 longSC.tex
add chisq test
add a reference and correct wording

%Recently, the ALICE Collaboration measured for the first time the Symmetric 2-harmonic 4-particle %Cumulants (SC), new multiparticle observables which quantify the relationship between event-by-%event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}. 
The first results for new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics, the \textit{Symmetric Cumulants}~(SC), were recently reported by the ALICE Collaboration~\cite{ALICE:2016kpq}.
The new observables are particularly robust against few-particle nonflow correlations and they provide independent, complementary information to recently analyzed symmetry plane correlators~\cite{Aad:2014fla}. 
It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of correlations between different order harmonics would constrain both the initial conditions and the medium properties~\cite{ALICE:2016kpq,Zhu:2016puf}.
In this article, we have extended the analysis of SC observables to higher order harmonics (up to $5^{\mathrm{th}}$ order) as well as to the measurement of the $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).  We also present a systematic comparison to hydrodynamic and AMPT model calculations.
In Sec.~\ref{sec:method} we summarize our findings from the previous work~\cite{ALICE:2016kpq} and present the analysis methods. The experimental setup and measurements are described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}. The results of the measurements are presented in Sec.~\ref{sec:results}. In Sec.~\ref{sec:theory} we present comparisons to model calculations.
%Various models used in this article are described in Sec.~\ref{sec:theory}. 
Finally, Sec.~\ref{sec:summary} summarizes our new results.

@@

The systematic uncertainty due to the track reconstruction procedure was estimated from comparisons between results for the so-called standalone TPC tracks with the 
same parameters as described in Sec.~\ref{sec:experiment}, and tracks from a combination of the TPC and the Inner Tracking System (ITS) detectors with tighter selection criteria.
To avoid non-uniform azimuthal acceptance due to dead zones in the SPD, and to get the best transverse momentum resolution, a hybrid track selection utilizing SPD hits and/or ITS refit tracks combined with TPC information was used.
Then each track reconstruction strategy was evaluated by varying the threshold on parameters used to select the tracks at the reconstruction level. 
A systematic difference of up to 12\% was observed in SC$(m,n)$ from the different track selections. 
In addition, we applied the like-sign technique to estimate nonflow contributions to SC$(m,n)$. The difference between results obtained by selecting all charged particles and results obtained after either selecting only positively or only negatively charged particles was the largest contribution to the systematic uncertainty and is about 7\% for SC(4,3) and 20\% for SC(5,3).

@@

We list here the important findings from the model comparisons to the centrality dependence of SC($m$,$n$) and NSC($m$,$n$):
\begin{enumerate}[(i)]
	\item The NSC(3,2) observable is sensitive mainly to the initial conditions, while the other observables are sensitive to both the initial conditions and the temperature dependence of $\eta/s$.
	\item The correlation strength between $v_3$ and $v_2$ and between $v_4$ and $v_3$ (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,3)) is significantly underestimated in hydrodynamic model calculations in mid-central collisions.
	%\item The sign of NSC(3,2) in 0--10\% central collisions was found to be different in the data and the hydrodynamic model calculations while the default AMPT model can reproduce it.
	\item All the VISH2+1 model calculations with large $\eta/s$ fail to capture the centrality dependence of the correlations regardless of the initial conditions.
	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions captures the data qualitatively, but not quantitively for most of the centrality ranges.
	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.
	%\item The hadronic rescattering in AMPT model makes the correlation strength (NSC) larger.
	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>~20\%$ within the errors. This hierarchy is reproduced well both by hydrodynamic and AMPT model calculations.

\end{enumerate}

>>>>

%Recently, the ALICE Collaboration measured for the first time the Symmetric 2-harmonic 4-particle %Cumulants (SC), new multiparticle observables which quantify the relationship between event-by-%event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}. 
The first results for new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics, the \textit{Symmetric Cumulants}~(SC), were recently reported by the ALICE Collaboration~\cite{ALICE:2016kpq}.
The new observables are particularly robust against few-particle nonflow correlations~\cite{Aamodt:2010pa} and they provide independent, complementary information to recently analyzed symmetry plane correlators~\cite{Aad:2014fla}. 
It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of correlations between different order harmonics would constrain both the initial conditions and the medium properties~\cite{ALICE:2016kpq,Zhu:2016puf}.
In this article, we have extended the analysis of SC observables to higher order harmonics (up to $5^{\mathrm{th}}$ order) as well as to the measurement of the $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).  We also present a systematic comparison to hydrodynamic and AMPT model calculations.
In Sec.~\ref{sec:method} we summarize our findings from the previous work~\cite{ALICE:2016kpq} and present the analysis methods. The experimental setup and measurements are described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}. The results of the measurements are presented in Sec.~\ref{sec:results}. In Sec.~\ref{sec:theory} we present comparisons to model calculations.
%Various models used in this article are described in Sec.~\ref{sec:theory}. 
Finally, Sec.~\ref{sec:summary} summarizes our new results.

@@

The systematic uncertainty due to the track reconstruction procedure was estimated from comparisons between results for the so-called standalone TPC tracks with the 
same parameters as described in Sec.~\ref{sec:experiment}, and tracks from a combination of the TPC and the Inner Tracking System (ITS) detectors with tighter selection criteria.
To avoid non-uniform azimuthal acceptance due to dead zones in the SPD, and to get the best transverse momentum resolution, a hybrid track selection utilizing SPD hits and/or ITS refit tracks combined with TPC information was used.
Then each track reconstruction strategy was evaluated by varying the threshold on parameters used to select the tracks at the reconstruction level. 
A systematic difference of up to 12\% was observed in SC$(m,n)$ from the different track selections. 
In addition, we applied the like-sign technique to estimate nonflow contributions~\cite{Aamodt:2010pa} to SC$(m,n)$. The difference between results obtained by selecting all charged particles and results obtained after either selecting only positively or only negatively charged particles was the largest contribution to the systematic uncertainty and is about 7\% for SC(4,3) and 20\% for SC(5,3).

@@

We list here the important findings from the model comparisons to the centrality dependence of SC($m$,$n$) and NSC($m$,$n$):
\begin{enumerate}[(i)]
	\item The NSC(3,2) observable is sensitive mainly to the initial conditions, while the other observables are sensitive to both the initial conditions and the temperature dependence of $\eta/s$.
	\item The correlation strength between $v_3$ and $v_2$ and between $v_4$ and $v_3$ (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,3)) is significantly underestimated in hydrodynamic model calculations in mid-central collisions.
	%\item The sign of NSC(3,2) in 0--10\% central collisions was found to be different in the data and the hydrodynamic model calculations while the default AMPT model can reproduce it.
	\item All the VISH2+1 model calculations with large $\eta/s$ fail to capture the centrality dependence of the correlations regardless of the initial conditions.
	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions captures the data qualitatively, but not quantitively for most of the centrality ranges.
	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.
	%\item The hadronic rescattering in AMPT model makes the correlation strength (NSC) larger.
	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>~20\%$ within the errors. This hierarchy is reproduced well both by hydrodynamic and AMPT model calculations.
\end{enumerate}

Finally, we perform a least-square test to the models for each SC observable via a log-likelihood or least squares-${\chi}^2$ method~\cite{PDBook} and the resulting ${\chi}^2$ values are discussed in Appendix~\ref{sec:chisq}.
